Real-Time Certified Probabilistic Pedestrian Forecasting

### 2017-02-16 pedestrian_forecasting_iros_2017.tex
small updates

Autonomous systems are increasingly being deployed in and around humans. 
The ability to accurately model and anticipate human behavior is critical to maximizing safety, confidence, and effectiveness of these systems in human-centric environments. 
The stochasticity of humans necessitates a probabilistic approach to capture the likelihood of an action over a set of possible behaviors. 
Since the set of plausible human behaviors is vast, this work focuses on anticipating the possible future locations of people within a bounded area. 
This problem is critical in many application domains such as enabling personal robots to navigate in crowded environments, managing pedestrian flow in smart cities, and synthesizing safe controllers for autonomous vehicles (AV).

@@

The output distributions of the three algorithms were compared using their integrals over the cells of a regular grid over our domain. 
These integrals are used to visualize the distributions in Figures \ref{fig:death-1-2} and \ref{fig:bookstore-1-2}.
%In keeping with our measurement model, the ground truth compared against was a grid that was identically zero except on a bounding box around the measurement at time $t$. 
%The ground truth bounding box at each time instance were set equal to the average bounding box dimension centered at the 
%were the average bounding box dimensions in the training data set. 
Because our predictions all share the same scale, we were able to amalgamate all of the prediction and truth values for all of the simulated agents at a given time step and generate ROC curves. 
Figure \ref{fig:auc_vs_time} shows the Area Under the Curve of these ROC curves versus time.
Our predictor behaves better than any of the other compared methods at moderately large $t$.
%, where we capture the behavior of the agent without suffering the misplaced confidence observed in Kitani et al.'s predictions. 
%Their encoding of velocity results in the prediction lagging behind the actual observed motion. 
This is despite providing the algorithm in \cite{Kitani2012} with the specific final location of each agent.
%Even given significantly better information, Kitani et al. generates lower quality predictions than our algorithm at all time scales.

>>>>

Autonomous systems are increasingly being deployed in and around humans. 
The ability to accurately model and anticipate human behavior is critical to maximizing safety, confidence, and effectiveness of these systems in human-centric environments. 
The stochasticity of humans necessitates a probabilistic approach to capture the likelihood of an action over a set of possible behaviors. 
Since the set of plausible human behaviors is vast, this work focuses on anticipating the possible future locations of pedestrians within a bounded area. 
This problem is critical in many application domains such as enabling personal robots to navigate in crowded environments, managing pedestrian flow in smart cities, and synthesizing safe controllers for autonomous vehicles (AV).

@@

The output distributions of the three algorithms were compared using their integrals over the cells of a regular grid over our domain. 
These integrals are used to visualize the distributions in Figures \ref{fig:bookstore-1-2} and \ref{fig:death-1-2}.
%In keeping with our measurement model, the ground truth compared against was a grid that was identically zero except on a bounding box around the measurement at time $t$. 
%The ground truth bounding box at each time instance were set equal to the average bounding box dimension centered at the 
%were the average bounding box dimensions in the training data set. 
Because our predictions all share the same scale, we were able to amalgamate all of the prediction and truth values for all of the simulated agents at a given time step and generate ROC curves. 
Figure \ref{fig:auc_vs_time} shows the Area Under the Curve of these ROC curves versus time.
Our predictor behaves better than any of the other compared methods at moderately large $t$.
%, where we capture the behavior of the agent without suffering the misplaced confidence observed in Kitani et al.'s predictions. 
%Their encoding of velocity results in the prediction lagging behind the actual observed motion. 
This is despite providing the algorithm in \cite{Kitani2012} with the specific final location of each agent.
%Even given significantly better information, Kitani et al. generates lower quality predictions than our algorithm at all time scales.
